### 2018-03-28 defectLocalization/paper/paper_body.tex
add project paper for defectlocalization

\section{Introduction}
Bug localization is one of the important steps in software maintenance.
Especially in issue triaging, where triager has to predict the potential defected components based on his understanding to the issue and to the system, and assign the issue to the right developer who has the required knowledge.
Automating this step helps speed up bugs fixing and reduce costs in issue triaging.
Lam \etal\cite{lam2017bug} proposed the state of the art approach to automate bug localization by ensemble rVSM\cite{zhou2012should} and DNN.  
Similar as most of the existed algorithms, this approach require source code information which is not always available to triagers or the QA team in large companies with code security requirement.
Analyzing the code base dramatically increase the learning time of this kind of algorithm in large projects.
Moreover, the fast evolution of source code further penalizes this approach that the predictive model has to be updated frequently.   
In this paper, we explore the possibility to predict defected components solely based on information learned from bug reports.

Recurrent neural network(RNN) has been proved to be efficient in capturing semantic as well as syntactic information from text to build statistical language models.
But for source code, Hellendoorn \etal show that the RNN is not better than traditional IR method in language model building\cite{hellendoorn2017deep}.
Bug report is different from common text and source code in that it is generally composed by common text and source code segment or error trace message. 
We believe that IR method and RNN can learn different information from bug reports and could complement each other.
Thus the ensemble of these two could offer better performance than using only one of them.

The contribution of this paper is in two folds:

### 2018-04-03 defectLocalization/paper/paper_body.tex
add text and citations

@@
 Bug localization is one of the important steps in software maintenance.
-Especially in issue triaging, where triager has to predict the potential defected components based on his understanding to the issue and to the system, and assign the issue to the right developer who has the required knowledge.
+Especially in issue triaging, where triager has to predict the potential defected components based on his understanding to the issue and the system, then he needs to assign the issue to the right developer who has the required knowledge to fix it.
 Automating this step helps speed up bugs fixing and reduce costs in issue triaging.
-Lam \etal\cite{lam2017bug} proposed the state of the art approach to automate bug localization by ensemble rVSM\cite{zhou2012should} and DNN.  
+Lam \etal\cite{lam2017bug} proposed the state of the art approach to automate bug localization by ensemble revised Vector Space Model(rVSM)\cite{zhou2012should} and Deep Neural Network(DNN).  
 Similar as most of the existed algorithms, this approach require source code information which is not always available to triagers or the QA team in large companies with code security requirement.
@@
 The contribution of this paper is in two folds:  
+\begin{itemize}
+	\item an ensemble of naive tf-idf based VSM and Gated Recurrent Network to recommend high risk components solely based on bug reports.
+	\item By analyzing the performence of the naive tf-idf based VSM and Gated Recurrent Network on their own, and the ensemble of these two, we show that IR method and RNN can learn different information from bug reports and could complement each other to offer better performance in the ensemble method.
+\end{itemize}
+
+\section{Background}
+\subsection{Bug Localization In Post-release Software Quality Insurrance}
+One of the main purpose of software engineering is to deliver high quality product to cients.
+However, as software architecture getting more and more complex, the possibility of introducing bugs in the development being higher and higher.  
+Different approaches are adopted in the industry to reduce the risk of delivering defeted product, test driven development, unit testing, test regression, peer review etc.
+But there are still bugs found by the client after release. 
+In this case, being able to fastly locate the defeted components and hence assign the rigth developer to fix the customer reported bugs is critical to post-release software quality insurrance.
+
+The traditional way is to do the assigning based on the triager's experience and his understanding of the reported issue. 
+For experienced triager, they could spot light some potential defected location very fast and accurate.
+But for triager with less experience or even new to the project, the process could take longer time and the prediction would not be correct.
+Thus they may assign a wrong developer for the issue and reassigning would be required and a longer time to get the bug fixed.
+
+To help address this problem, recent research applies NLP techniques to learn from bug reports and suggest a ranked list of potential defect location\cite{gay2009use}\cite{lam2017bug}\cite{nguyen2011topic}\cite{zhou2012should}\cite{saha2013improving}\cite{shokripour2013so}, or to suggest the developer who could fix the bug\cite{anvik2011reducing}\cite{bhattacharya2010fine}\cite{xuan2012developer}\cite{jonsson2016automated}.
+All these approaches focus on combining source code and code change history from version controling tools(ex: Git)  with bug reports to make the prediction.
+However, in companies that has a strict source code security policy, which is a common situation for large companies, source code or even code change history is not available for triagers. 
+Bug report is the only source of information they can use to perform the triaging.   
+Therefore, in this work we focus on bug localization with only bug reports as the input source.
+
+\subsection{Information Retrieval From Bug Report}
+
+\section{Methodology}
+
+\subsection{Vector Space Model}
+
+\subsection{TF-IDF}
+
+\subsection{Gated Recurrent Unit}
+
+\subsection{Ensemble of VSM and GRU}
+
+\section{Experiment Design}
+
+\subsection{Data Set and Preprocessing}
+
+\subsection{Metrics}
+
+\section{Evaluation and Discussion}
+
+\subsection{Evaluation Result}
+
+\subsection{Is RNN Better Than IR Methods in Mining Bug Report ?}
+
+\subsection{title}

### 2018-04-03 defectLocalization/text_classification.py
update code

@@ -25,6 +25,8 @@ from tensorflow.contrib import rnn # use for old version tensorflow
 #from utils import seed, db, loadDataframe
 from util_m import * 
 from sklearn.cross_validation import train_test_split
+from sklearn.feature_extraction.text import TfidfVectorizer
+import nltk
 
 FLAGS = tf.app.flags.FLAGS
 tf.app.flags.DEFINE_bool('test_with_fake_data', False,
@@ -34,6 +36,10 @@ MAX_DOCUMENT_LENGTH = 250
 EMBEDDING_SIZE = 100
 n_words = 0
 save_path = "./output.log"
+def tokenizer(text):
+    words = nltk.word_tokenize(text)
+    return words
+
 def bag_of_words_model(x, y, mode, params):
     """A bag-of-words model. Note it disregards the word order in the text."""
     target = tf.one_hot(y, params.get("classes", 15), 1, 0)
@@ -54,9 +60,10 @@ def rnn_model(x, y, mode, params):
     # This creates embeddings matrix of [n_words, EMBEDDING_SIZE] and then
     # maps word indexes of the sequence into [batch_size, sequence_length,
     # EMBEDDING_SIZE].
-    word_vectors = learn.ops.categorical_variable(x, n_classes=n_words,
+    word_vectors = learn.ops.categorical_variable(x['x'], n_classes=n_words,
                                                   embedding_size=EMBEDDING_SIZE, name='words')
     
+
     # Split into list of embedding per word, while removing doc length dim.
     # word_list results to be a list of tensors [batch_size, EMBEDDING_SIZE].
     word_list = tf.unstack(word_vectors, axis=1)
@@ -66,8 +73,13 @@ def rnn_model(x, y, mode, params):
     target = tf.one_hot(y, params.get("classes", 15), 1, 0)
  #   yield(batch_size)
     # Create a Gated Recurrent Unit cell with hidden size of EMBEDDING_SIZE.
-    cell =tf.contrib.rnn.GRUCell(EMBEDDING_SIZE)
+    def make_cell():
+        cell =tf.contrib.rnn.GRUCell(EMBEDDING_SIZE)
+        cell = tf.contrib.rnn.DropoutWrapper(cell, output_keep_prob=0.5)
+        return cell
 
+    cell = tf.contrib.rnn.MultiRNNCell(
+        [make_cell() for _ in range(10)], state_is_tuple=False)
     # Create an unrolled Recurrent Neural Networks to length of
[…]

### 2018-04-03 defectLocalization/util_m.py

@@ -1,4 +1,5 @@
 import xmltodict
+import re
 def get_data(path):
     with open(path,'r') as f:
         doc = xmltodict.parse(f.read())
@@ -6,12 +7,18 @@ def get_data(path):
 
 def get_single_record(record,in_list):
     info = record['buginformation']
+    clean_info = info['description'].replace("."," ")
+    clean_info = clean_info.replace("/"," ")
+    clean_info = clean_info.replace("_"," ")
+
+    clean_info = re.sub(r"\d+" ,"",clean_info)
+    clean_info = re.sub(r"[\[\]\{\}\#\$\^\%]" ," ",clean_info)
     bug_id=record['@id']
     fixed_files = record['fixedFiles']['file']
     if isinstance(fixed_files, basestring):
        splited_file = fixed_files.split('.')
        if len(splited_file)>2:
-           in_list.append([bug_id,info['summary'],info['description'].replace("."," "),[".".join(splited_file[:-2])]])
+           in_list.append([bug_id,info['summary'],clean_info,[".".join(splited_file[:-2])]])
     else:
        splited_files = []
        for f in fixed_files:
@@ -19,7 +26,7 @@ def get_single_record(record,in_list):
            if len(splited_file)>2:
                splited_files.append(".".join(splited_file[:-2]))
           
-       in_list.append([bug_id,info['summary'],info['description'].replace("."," "),splited_files])
+       in_list.append([bug_id,info['summary'],clean_info,splited_files])
     return 0
 def get_flat_record(record, in_list):
 

### 2018-04-04 defectLocalization/paper/paper_body.tex
add text to paper

@@
 Thus they may assign a wrong developer for the issue and reassigning would be required and a longer time to get the bug fixed. 
+Jeon \etal\\cite{jeong2009improving} reported that the Eclipse project takes on average 40 days for bug assignment and another 100 days for reassigning..
+The numbers for Mozilla are 180 days for the first assigning and another 250 days for reassigning.
 
@@
 
-\subsection{Information Retrieval From Bug Report}
+\subsection{Data Mining Bug Reports}
+The most popular technique used in information retrieval from bug reports is the VSM with TF-IDF as entry value\cite{gay2009use}\cite{zhou2012should}. 
+Another frequent used algorithm is the Latent Dirichlet Allocation(LDA)\cite{nguyen2011topic}.
+And resent works try to ensemble IR techniques with Machine Learning to achieve better performance\cite{jonsson2016automated}\cite{lam2017bug}.
+Jonsson \etal \cite{jonsson2016automated} ensemble TF-IDF with different ML algorithms with Stacked Generalization. 
+Lam \etal\ \cite{lam2017bug}combines rVSM with DNN.
+
+To the best of our knowledge, there is not past work to use DNN, more specifically deep Recurrent Neural Network independently to learn from bug reports and suggest potential defect location.
+In this work, we apply DNN with multiple layers of Gated Recurrent Unit to learning from bug reports, and compare its performance to VSM.
+Moreover, we ensemble the DNN with VSM to leverage the performance.
 
@@
 \subsection{Vector Space Model}
+Vector Space Model was first proposed by Salton \etal\cite{salton1975vector} to quantify documents.
+With a pre-defined and indexed vocabulary of size $s$: $V = \{t_1, t_2,...,t_s\}$, 
+each term $t_i$ in a given document $d$ could be represented by a weight quantity $w_i$, where $i$ is its index in the vocabulary $V$.
+Thus the given document $d$ could be represented by a vector $d=[w_1,w_2,...,w_s]$.
+Obviously, the length of the vector $d$ is the same as the size of the vocabulary.
+If a term $t_j$ is not in document $d$, then $w_j = 0$.   
+With this vector representation, we can analyze the documents with quantitative methods.
 
 \subsection{TF-IDF}
+The selection of weighting method to use in VSM is important to the performance. 
+We choose TF-IDF\cite{salton1988term} because of its well reported performance in previous works.
+TF is short for term frequency. 
+There are different schemes to evaluate TF, in our implementation, we calcuate TF by fomular 1
 
-\subsection{Gated Recurrent Unit}
+\begin{equation}
+	tf(t,d) = f_{t,d}
+\end{equation}
+
+where $t$ is the given term, $d$ is the document and $f_{t,d}$ is the count of term $t$ in document $d$.
+
+IDF is short for Inverse Document Frequency and is generated from equation 2in our implementation.
+
+\begin{equation}
+	idf(t) = log\frac{n_d}{df(d,t)} +1
+\end{equation}
+where $n_d$ is the total of documents and $df(d,t)$ is the number of documents containing term $t$.
+
+Then the weight $w_t$ is given by:
+\begin{equation}
+	w_t = tf(t)*idf(t)
+\end{equation}
+
+Then the resulting vector $w$ is normalized to get the vector $d$:
+\begin{equation}
+	d = \frac{w}{||w||_2} = \frac{w}{\sqrt{\sum_{i=1}^{s}w_i^2}}
+\end{equation}
+
+\subsection{Our VSM Bug Localization Model}
+Similar as the how to rank risky files based on similar bugs in rVSM\cite{zhou2012should},
+after we obtain the vector representation of all bug reports, for a new comming report $d_n$ and an old bug report $d_i$ that has been fixed in the training set $D$ , we calculate their Cosine similarity:
+\begin{equation}
+	similarity(d_n,d_i) = \frac{d_n \cdot d_i}{||d_n||*||d_i||}
+\end{equation}
+
+For a given component $c$, define $D_c$ to be the set of bugs that are fixed by changing code in $c$,  then the risk of $c$ is given by:
+\begin{equation}
+	risk(c) = min(similarity(d_n,d_i)) \forall d_i \in D_c
+\end{equation}
+
+And the components are ranked by their risk score from maximum to minimum.
+\todo{report performance briefly}
+
+\subsection{Deep Gated Recurrent Unit Network}
+Recurrent Neural Network(RNN) is good at modeling sequential data. 
+As Mikolov introduced RNN to language modeling\cite{mikolov2010recurrent}, more and more applications of RNN in document analysis related task are proposed, for example, machine translation. 
+In recent years, people starts to apply RNN to model source code\cite{raychev2014code}. 
+It is believed that RNN can learn syntactic and semantic rules from text documents.
+Given that bug reports are also written by human natural language, we believe that we can use RNN to learn from bug reports and make precise predictions on risky components.
+We apply Gated Recurrent Unit in our RNN implementation.
+GRU is proposed to solve the gradient vanishing problem in training a (RNN)\cite{chung2014empirical}.
+It acheive the same performance as Long Short Term Memory but with less computations.
+Its stucture is show in figure \ref{gru}. $h$ is the current state and $\hat{h}$ is context state which could memorize the impact of the input history. 
+The reset gate $r$ controls whether the state from the current input should be memorized in $\hat{h}$.
+The update gate $z$ controls whether the memory from $\hat{h}$ should considered when updating $h$ to give out prediction.  
+\begin{figure}
+	\includegraphics[scale=0.5]{gru.png}
+	\caption{Gated Recurrent Unit\cite{chung2014empirical}}
+	\label{gru}
+\end{figure}
+
+Given the input vector $x_t$ at step t, each gates and states are calcuated recursively as:
+\begin{equation}
+	z_t = \sigma_g(W_zx_t+U_{z}h_{t-1}+b_z)
+\end{equation}	
+\begin{equation}
+	r_t =  \sigma_g(W_rx_t+U_{r}h_{t-1}+b_r)
+\end{equation}	
+\begin{equation}
+	h_t=(1-z_t) \circ h_{t-1} + z_t \circ \sigma_h(W_hx_t+U_{h}(r_t \circ h_{t-1})+b_h)
+\end{equation}
+Where $o$ is point-wise multiplication, $W$ and $U$ is the weight matrices for the corresponding component, $b$ is the bias vector.
+$\sigma_g$ is the sigmoid activation function which has the form:
+\begin{equation}
+	\sigma_g(x) = \frac{1}{1+e^{-1}}
+\end{equation}
+and $\sigma_h$ is the hyperbolic tangent activation function with the form:
+\begin{equation}
+\sigma_h(x)=\frac{e^x - e^{-x}}{e^x + e^{-x}}	
+\end{equation}
+
+In our DRNN implementation, the input layer pass the input vector to the embedding layer which generates the embedding of size $100$.
+The resulted embedding will then be passed to the stacked hidden GRU layers of size $10$.
+The encoding of the GRU hidden layers is pass to fit a logistic regression to predict the possibility of each components to be defected.
+\todo{draw the graph to show the deep structure}
+
+The number of layers and the embedding size is selected randomly. 
+Increasing the number of layers could improve performance a litter with longer training time as penalty.
+Small change to the embedding size does not change the result siginicantly
+Large change (ex: doubling the embedding size) would result in huge memory requirement and failed in runtime.
+\todo {report performance }
 
 \subsection{Ensemble of VSM and GRU}
+Ensemble method \cite{dietterich2000ensemble} is used to combine predictions from multiple different model to give out better performance than a single model.	
+\cite{lam2017bug} ,\cite{wang2014version} and \cite{jonsson2016automated} apply ensemble method to perform bug triage and achieve good performance. 
+Different schemes can be used in ensembling. 
+Stacked Generalization\cite{wolpert1992stacked} is theorectally the most effective one which adds one more classifier to take predictions from ensembled models as input and is trained to reduce prediction error.
+Jonsson \etal \cite{jonsson2016automated} ensembled TF-IDF with different ML algorithms with Stacked Generalization.
+However, as a preliminary research, we apply a simlper scheme 
+For a given component, we takes the minimum of the two risks given by the two aforemention models as the final risk.
+
+\begin{equation}
+risk(c) = min(risk_{VSM}(c) , risk_{DNN}(c) )
+\end{equation}
+
+\todo {report performace}
 
@@
 
-\subsection{Data Set and Preprocessing}
+\subsection{Data Set }
+We perform our experiment on the exact same data set used in \cite{wang2014version} ,\cite{saha2013improving} and \cite{zhou2012should}.
+The detail of the data set is summarized in table
+
+\todo {make the table}
+
+There are in total 3,379 bug reports from four popular open source projects in this data set, AspectJ, Eclipse, SWT, and ZXing. 
+For each bug report, we can obtain its title, description from the issue reporter, and the files being changed to fixed the reported bug. 
+ZXing, a barcode image processing library for Android platform, is the smallest data set.
+It contains 20 bugs fixed between March and September 2010 with 391 source files being changed.
+SWT is an open source widget tookit. 
+This data set has 98 bugs fixed from October 2004 to April 2010 with 484 source files being fixed. 
+Eclipse, the famous open source integrated development environment, contains 3075 bugs fixed in the period between October 2004 and March 2011 with 12863 files being changed.
+
+Differently from previous work, the granularity of our experiment is on component level instead of on file level. 
+Because we don't use the source code information to simulate a situation of strict source code security, new added files cannot be captured in the prediction with either VSM or DNN.
+Thus we first truncate the path of a given file by removing the file name to obtain the component containing the given file. 
+We assume that by knowing the potential defected component is enough for assigning the appropriate developer to solve the issue.
+Because if a developer knows a component very well, he should also has knowledge to the new added file to that component.
+After the truncation, there are\todo{add number} , , , , components in ZXing , SWT, Eclipse and AspectJ respectively. 
+We didn't perform our experiment on the project AspectJ, since there are only two components in this data set, the result was highly inflated . 
+The detail of the three data sets is summarized in table \todo{make the data set table}
+
+\subsection{Preprocessing}
 
@@
 
-\subsection{Is RNN Better Than IR Methods in Mining Bug Report ?}
+%\subsection{Is RNN Better Than IR Methods in Mining Bug Report ?}
 
-\subsection{title}
+%\subsection{Is Ensembling Really Improve Performance}

### 2018-04-04 defectLocalization/paper/paper_body.tex
-add text

@@
 After the truncation, there are\todo{add number} , , , , components in ZXing , SWT, Eclipse and AspectJ respectively. 
-We didn't perform our experiment on the project AspectJ, since there are only two components in this data set, the result was highly inflated . 
+For the project AspectJ, since there are only two components in this data set, the result was highly inflated.
+Thus we perform the experiment on file level for the project AspecJ. 
 The detail of the three data sets is summarized in table \todo{make the data set table}

### 2018-04-04 defectLocalization/paper/paper_body.tex
add text

--- 2018-04-04 defectLocalization/paper/paper_body.tex
@@
 We perform our experiment on the exact same data set used in \cite{wang2014version} ,\cite{saha2013improving} and \cite{zhou2012should}.
-The detail of the data set is summarized in table
-
-\todo {make the table}
+The detail of the data set is summarized in table \ref{data_table}
 
 There are in total 3,379 bug reports from four popular open source projects in this data set, AspectJ, Eclipse, SWT, and ZXing. 
+\begin{itemize}
+	\item ZXing, a barcode image processing library for Android platform, is the smallest data set.
+	It contains 20 bugs fixed between March and September 2010 with 391 source files being changed.
+	\item SWT is an open source widget tookit. 
+	This data set has 98 bugs fixed from October 2004 to April 2010 with 484 source files being fixed. 
+	\item AspecJ, An aspect-oriented extension to the Java programming language 
+	\item Eclipse, the famous open source integrated development environment, contains 3075 bugs fixed in the period between October 2004 and March 2011 with 12863 files being changed.
+\end{itemize}
+
 For each bug report, we can obtain its title, description from the issue reporter, and the files being changed to fixed the reported bug.
-ZXing, a barcode image processing library for Android platform, is the smallest data set.
-It contains 20 bugs fixed between March and September 2010 with 391 source files being changed.
-SWT is an open source widget tookit. 
-This data set has 98 bugs fixed from October 2004 to April 2010 with 484 source files being fixed. 
-Eclipse, the famous open source integrated development environment, contains 3075 bugs fixed in the period between October 2004 and March 2011 with 12863 files being changed.
 
@@
 After the truncation, there are\todo{add number} , , , , components in ZXing , SWT, Eclipse and AspectJ respectively. 
-We didn't perform our experiment on the project AspectJ, since there are only two components in this data set, the result was highly inflated . 
-The detail of the three data sets is summarized in table \todo{make the data set table}
+We removed one bug from the SWT project since the defected file has no component level, it locates in the top most directory. 
+Removing one record does not impact on the performance evaluation given the relatively large number of bugs. 
+The detail of the three data sets is summarized in table \ref{data_table}
 
 \subsection{Preprocessing}
+Bug reports is different from normal text in that it could has code elements, source file names or error log in its content. 
+Here we list some examples to illustrate the situation. 
+This is some bug description from the Eclipse project:
+
+\textbf{Bug 77046:}If the Pattern Match job is already running when the console's partitioner reports that it is finished work, it is possible that the pattern matcher can think that it's finished before checking the entire document.
+This is the trace from the failed test: Incorrect number of messages logged for build.
+Should be 8.
+Was 2 junit.framework.AssertionFailedError: Incorrect number of messages logged for build.
+Should be 8.
+Was 2 at\\ org.eclipse.ant.tests.ui.BuildTests.testOutput(BuildTests.java:41) at\\ sun.reflect.NativeMethodAccessorImpl.invoke0(Native Method) at\\ sun.reflect.NativeMethodAccessorImpl.invoke\\(NativeMethodAccessorImpl.java:39) at\\ sun.reflect.DelegatingMethodAccessorImpl\\.invoke(DelegatingMethodAccessorImpl.java:25) at\\ org.eclipse.ant.tests.ui.AbstractAntUIBuildTest.access\$0\\(AbstractAntUIBuildTest.java:1) at\\ org.eclipse.ant.tests.ui.AbstractAntUIBuildTest\$1\\.run(AbstractAntUIBuildTest.java:44) at\\ java.lang.Thread.run(Thread.java:534)
+
+After the normal text describing the issue, the reporter also attached the error trace log as well.
+If we don't perform the preprocessing correctly, neither VSM or DRNN model could learn patterns from the error trace log, since the long component name would be seen as one term, but actually there are multiple important terms there.
+For example, the path\\ "org.eclipse.ant.tests.ui.BuildTests.testOutput(BuildTests.java:41)"\\ contains important terms: ui,Build,Test. Here is another example:
+
+\textbf{Bug 76208}
+Boolean.getBoolean((String)newValue) queries if a system property exists with the argument name...not what we want in this context.
+
+The reporter is reporting an undesired functionality from a code segment. Again important terms would be missed if we don't separate the code segment correctly.
+
+Thus we replace all non word character by white space to separate terms, and if a small case character followed by an upper case character, the separate them by a white space. 
+We also remove all numbers to reduce the size of the vocabulary and hence the requirement on computation resource. 
+After the preprocessing, we summarize the data set detail in table \ref{data_table}.We apply the 80-20\% split to generate the training and testing set for each project.
+
+\begin{table*}[!tbh]
+	\begin{center}
+		\caption{Data Set Summary}
+		\label{data_table}
+
+		\begin{tabular}{c|l|l|l|l|l} %
+			\textbf{Project} & \textbf{Description} & \textbf{\#bugs} & \textbf{period} & \textbf{\#files} & \textbf{\#component}\\
+			\hline\hline
+			ZXing & barcode image processing  & 20 & 2010.3-& 391 &11\\
+                  &library  for Android platform & &  2010.10 & & \\			
+			SWT & open source widget & 98 & 2004.10-& 484 &15\\
+			v3.1 &  tookit & &2010.4 & &\\
+			AspecJ & An aspect-oriented  & 286 &2002.6 & 6485 & 534\\
+			       &   extension to the Java & & -2006.10 & &\\
+			       &    programming language & & & &\\
+			Eclipse & open source integrated& 3075&2004.10- & 12863& 555\\
+ 			 v3.1 &  development environment& &2011.3 &  &\\
+		\end{tabular}
+	\end{center}
+\end{table*}
 
 \subsection{Metrics}
+To evaluate the performance of different models, we apply the following common used metrics:
 
+\textbf{Top-k Bugs Hit}
+Top-k bugs hit is the number of bugs that are correctly localized from the top k components in the output ranked list. 
+At least one component has to been captured in the top k list for the given prediction be classified as a hit.
+
+\textbf{Mean Reciprocal Rank(MRR)} is a measure to evaluate the quality of the ranked list from a recommendation system. 
+If for all queries under test, the higer the the first hit relevant item is ranked, the higher value the MRR will be and vice versus. 
+It's calculated by the following formula:
+\begin{equation}
+MRR = \frac{1}{|Q|}\sum^{i \in Q}\frac{1}{rank_i}
+\end{equation} 
+Where $Q$ is the set of test queries, in our context would be the bugs in the testing data set. 
+$i$ is a particular bug in $Q$ and $rank_i$ is the ranking of the first collect prediction in the output list.
+
+MRR only cares about the ranking of the first correct prediction. 
+However, there could be multiple defected components for one reported bug. 
+We also need to check how well different models rank the other defected components.
+
+\textbf{Mean Average Precision(MAP)} To evaluate how well different models rank all defected components we first calculate the average precision for one bug report:
+ \begin{equation}
+ 	AP=\frac{1}{|C|} \sum_{i=1}^{N}prec(i)*relevance(i)
+ \end{equation}
+Where $C$ is the set of all defected components for the given bug. 
+$N$ is the total number of components in the system.  
+$prec(i)$ is the precision for the top-i list.
+$relevance(i)$ is 1 if the $i^{th}$ item is defected, otherwise $0$.
+
+Then MAP is calculated by the equation:
+\begin{equation}
+	MAP = \frac{1}{|Q|}\sum^{Q_i \in Q}AP(Q_i)
+\end{equation}
+
+The model with higher MAP score is the better.
 \section{Evaluation and Discussion}
 
-\subsection{Evaluation Result}
+\subsection{Experiment Result}
 
-%\subsection{Is RNN Better Than IR Methods in Mining Bug Report ?}
+The performance of the VSM model is summarized in table \ref{performance_vsm}, we report the top k hit value with k equals 1,5 and 10.
+
+ \begin{table}[h]
+ 	\begin{center}
+ 		\caption{Performance Of VSM with TF-IDF}
+ 		\label{performance_vsm}
+
+ 		\begin{tabular}{c|l|l|l|l|l} %
+ 			\textbf{Project} & \textbf{Top 1} & \textbf{Top 5} & \textbf{Top 10} & \textbf{MRR} & \textbf{MAP}\\
+ 			\hline\hline
+ 			ZXing & 1(25\%)& 2(50\%) &4(100\%)& 43.125\% &39.27\%\\
+
+ 			SWT & 1(5\%) & 6(30\%) & 10(50\%)& 19.46\% & 10.73\%\\
+
+ 			AspecJ & 3(5.17\%)  & 15(25.86\%) &24(41.38\%) & 14.40\% & 5.74\%\\
+
+ 			Eclipse &7(1.15\%) & 17(2.78\%)& 22(3.6\%) & 2.37\%& 1.17\%\\
+
+ 		\end{tabular}
+ 	\end{center}
+ \end{table}
+
+\subsection{Is RNN Better Than IR Methods in Mining Bug Report ?}
 

### 2018-04-05 defectLocalization/paper/paper_body.tex
add performance table

@@
 
-The performance of the VSM model is summarized in table \ref{performance_vsm}, we report the top k hit value with k equals 1,5 and 10.
+We report the performance of the three models in table \ref{performance_top_k} .
+For the project Zxing and SWT, because the their total of components is close to 10, we report the top-1 bug hit rate.
+For the project AspectJ and Eclipse, given the their large  number of components, we report the top-10 bug hit rate.
 
@@
  	\begin{center}
- 		\caption{Performance Of VSM with TF-IDF}
- 		\label{performance_vsm}
+ 		\caption{Top k bugs hit}
+ 		\label{performance_top_k}
 
- 		\begin{tabular}{c|l|l|l|l|l} %
- 			\textbf{Project} & \textbf{Top 1} & \textbf{Top 5} & \textbf{Top 10} & \textbf{MRR} & \textbf{MAP}\\
+ 		\begin{tabular}{c|l|l|l} %
+ 			 \textbf{Projects} & \textbf{VSM} & \textbf{DRNN} & \textbf{Ensemble} \\
  			\hline\hline
- 			ZXing & 1(25\%)& 2(50\%) &4(100\%)& 43.125\% &39.27\%\\
+ 			ZXing(top-1)& 4(100\%)&4(100\%) &4(100\%) \\
 
- 			SWT & 1(5\%) & 6(30\%) & 10(50\%)& 19.46\% & 10.73\%\\
+ 			SWT(top-1) & 10(50\%) & 20(100\%) &18(90\%)\\
 
- 			AspecJ & 3(5.17\%)  & 15(25.86\%) &24(41.38\%) & 14.40\% & 5.74\%\\
+ 			AspecJ(top-10) & 24(41.38\%)  & 46(79.31\%) & 28(48.28)\%\\
 
- 			Eclipse &7(1.15\%) & 17(2.78\%)& 22(3.6\%) & 2.37\%& 1.17\%\\
+ 			Eclipse(top-10) &22(3.6\%) & 124(20.29\%)& 26(4.26\%)\\
+
+ 		\end{tabular}
+ 	\end{center}
+ \end{table}
+
+ \begin{table}[h]
+ 	\begin{center}
+ 		\caption{Mean Reciprocal Rank(MRR)}
+ 		\label{performance_MRR}
+
+ 		\begin{tabular}{c|l|l|l} %
+ 			\textbf{Projects} & \textbf{VSM} & \textbf{DRNN} & \textbf{Ensemble} \\
+ 			\hline\hline
+ 			ZXing& 43.12\%&34.16\% &52.62\% \\
+
+ 			SWT & 19.45\% & 67.92\% & 58.63\% \\
+
+ 			AspecJ &14.40\%  & 44.10 \% & 46.22\%\\
+
+ 			Eclipse &2.38\% & 11.81\%& 4.12\% \\
+
+ 		\end{tabular}
+ 	\end{center}
+ \end{table}
+
+ \begin{table}[h]
+ 	\begin{center}
+ 		\caption{Mean Average Precision(MAP)}
+ 		\label{performance_map}
+
+ 		\begin{tabular}{c|l|l|l} %
+ 			\textbf{Projects} & \textbf{VSM} & \textbf{DRNN} & \textbf{Ensemble} \\
+ 			\hline\hline
+ 			ZXing& 39.27\%&30.83\% &51.77\%\\
+
+ 			SWT & 10.73\%  & 51.13\%  & 39.71\% \\
+
+ 			AspecJ &5.74\% & 21.39\% & 15.69\%\\
+
+ 			Eclipse &1.18\% & 6.53\%& 1.97\% \\
 

### 2018-04-05 defectLocalization/paper/paper_body.tex
Update paper_body.tex
add some text to evaluation

@@
 
-We report the performance of the three models in table \ref{performance_top_k} .
-For the project Zxing and SWT, because the their total of components is close to 10, we report the top-1 bug hit rate.
-For the project AspectJ and Eclipse, given the their large  number of components, we report the top-10 bug hit rate.
+We report the performance of the three models in table \ref{performance_top_k}, \ref{performance_MRR} and \ref{performance_map}.
+For the project Zxing and SWT, because the total of  their components is close to 10, we report the top-1 bug hit rate.
+For the project AspectJ and Eclipse, given the large  number of components, we report the top-10 bug hit rate.
+As shown in Table \ref{performance_top_k}, All models acheive 100\%  bug hit for the project ZXing, DRNN achieves the best result in all other three projects.
+It gets 100\%, 79.31\% and 20.29\% hit rate for the project SWT, AspectJ and Eclipse respectively.
+VSM achieves the lowest bug hit rate which is 50\%, 41.38\% and 3.6\% for SWT, AspectJ and Eclipse respectively. 
+DRNN achieve 163.82\% more bugs hit on average than VSM.
 
@@
 
- 			SWT(top-1) & 10(50\%) & 20(100\%) &18(90\%)\\
+ 			SWT(top-1) & 10(50\%) & \textbf{20(100\%)} &18(90\%)\\
 
- 			AspecJ(top-10) & 24(41.38\%)  & 46(79.31\%) & 28(48.28)\%\\
+ 			AspecJ(top-10) & 24(41.38\%)  & \textbf{46(79.31\%)} & 28(48.28)\%\\
 
- 			Eclipse(top-10) &22(3.6\%) & 124(20.29\%)& 26(4.26\%)\\
+ 			Eclipse(top-10) &22(3.6\%) & \textbf{124(20.29\%)} & 26(4.26\%)\\
 
@@
  \end{table}
+
+As shown in Table \ref{performance_MRR}, VSM achieves the best MRR of 43.12\% for ZXing, but DRNN achieves the best MRR in all other three projects which are 67.92\%, 44.10\% and 11.81\% for SWT, AspectJ and Eclipse respectively.
+DRNN achieve 163.82\% more bugs hit on average than VSM.
 

### 2018-04-06 defectLocalization/util_m.py
sync repo

@@ -12,17 +12,25 @@ def get_single_record(record,in_list):
     clean_info = clean_info.replace("_"," ")
 
     clean_info = re.sub(r"\d+" ,"",clean_info)
-    clean_info = re.sub(r"[\[\]\{\}\#\$\^\%]" ," ",clean_info)
+    clean_info = re.sub(r"[^\W]" ," ",clean_info)
+    pattern = re.compile(r'[a-z][A-Z]')
+    cat = pattern.search(clean_info)
+    while(cat is not None):
+        i = cat.start()+1
+        clean_info = clean_info[:i]+ " " +clean_info[i:]
+        cat = pattern.search(clean_info)
     bug_id=record['@id']
     fixed_files = record['fixedFiles']['file']
     if isinstance(fixed_files, basestring):
-       splited_file = fixed_files.split('.')
+       splited_file = fixed_files.replace('/','.')
+       splited_file = splited_file.split('.')
        if len(splited_file)>2:
            in_list.append([bug_id,info['summary'],clean_info,[".".join(splited_file[:-2])]])
     else:
        splited_files = []
        for f in fixed_files:
-           splited_file = f.split('.')
+           splited_file = f.replace('/','.')
+           splited_file = splited_file.split('.')
            if len(splited_file)>2:
                splited_files.append(".".join(splited_file[:-2]))
           

### 2018-04-06 language_modeling/ptb_word_lm.py

@@ -52,7 +52,7 @@ $ tar xvf simple-examples.tgz
 
 To run:
 
-$ python ptb_word_lm.py --data_path=simple-examples/data/
+$ python ptb_word_lm.py --data_path=simple-examples/data/ --num_gpus=0 --save_path=/home/zhuyuecai/workspace/AITour/language_modeling/model_word_lstm/ --model=large
 
 """
 from __future__ import absolute_import
@@ -208,6 +208,11 @@ class PTBModel(object):
     if config.rnn_mode == BLOCK:
       return tf.contrib.rnn.LSTMBlockCell(
           config.hidden_size, forget_bias=0.0)
+    if config.rnn_mode== ELMAN:
+      return tf.contrib.rnn.BasicRNNCell(
+          config.hidden_size,  state_is_tuple=True,
+          reuse=not is_training)
+
     raise ValueError("rnn_mode %s not supported" % config.rnn_mode)
 
   def _build_rnn_graph_lstm(self, inputs, config, is_training):
@@ -445,6 +450,8 @@ def get_config():
 
 def main(_):
   per_list = []
+  val_list= []
+  test_list =[]
   if not FLAGS.data_path:
     raise ValueError("Must set --data_path to PTB data directory")
   gpus = [
@@ -518,15 +525,32 @@ def main(_):
         per_list.append(train_perplexity)
         print("Epoch: %d Train Perplexity: %.3f" % (i + 1, train_perplexity))
         valid_perplexity = run_epoch(session, mvalid)
+        val_list.append(valid_perplexity)
         print("Epoch: %d Valid Perplexity: %.3f" % (i + 1, valid_perplexity))
 
       test_perplexity = run_epoch(session, mtest)
       print("Test Perplexity: %.3f" % test_perplexity)
-
+      test_list.append(test_perplexity)
       if FLAGS.save_path:
         print("Saving model to %s." % FLAGS.save_path)
         sv.saver.save(session, FLAGS.save_path, global_step=sv.global_step)
   with open("./output.log",'w') as f:
+      f.write("train perplexity:\n")
       f.write(per_list)
+      for item in per_list:
+        f.write("%s," % item)
+      f.write("/n")
+      f.write("="*12)
+      f.write("validation perplexity:\n")
+      for item in val_list:
+        f.write("%s," % item)
+      f.write("/n")
+      f.write("="*12)
+      f.write("test perplexity:\n")
+      f.write(test_list)
[…]

### 2018-04-06 language_modeling/reader.py

@@ -71,9 +71,9 @@ def ptb_raw_data(data_path=None):
     where each of the data objects can be passed to PTBIterator.
   """
 
-  train_path = os.path.join(data_path, "ptb.char.train.txt")
-  valid_path = os.path.join(data_path, "ptb.char.valid.txt")
-  test_path = os.path.join(data_path, "ptb.char.test.txt")
+  train_path = os.path.join(data_path, "ptb.train.txt")
+  valid_path = os.path.join(data_path, "ptb.valid.txt")
+  test_path = os.path.join(data_path, "ptb.test.txt")
 
   word_to_id = _build_vocab(train_path)
   train_data = _file_to_word_ids(train_path, word_to_id)

### 2018-04-11 defectLocalization/paper/paper_body.tex
add code change and text to paper

@@
 Thus they may assign a wrong developer for the issue and reassigning would be required and a longer time to get the bug fixed. 
-Jeon \etal\\cite{jeong2009improving} reported that the Eclipse project takes on average 40 days for bug assignment and another 100 days for reassigning..
+Jeon \etal \cite{jeong2009improving} reported that the Eclipse project takes on average 40 days for bug assignment and another 100 days for reassigning..
 The numbers for Mozilla are 180 days for the first assigning and another 250 days for reassigning.
@@
 \subsection{Our VSM Bug Localization Model}
-Similar as the how to rank risky files based on similar bugs in rVSM\cite{zhou2012should},
+Similar as how to rank risky files based on similar bugs in rVSM\cite{zhou2012should},
 after we obtain the vector representation of all bug reports, for a new comming report $d_n$ and an old bug report $d_i$ that has been fixed in the training set $D$ , we calculate their Cosine similarity:
@@
 And the components are ranked by their risk score from maximum to minimum.
-\todo{report performance briefly}
+Our VSM model achieve a MRR of 43.12\%, 19.45\%, 14.40\% and 2.38\%, and a MAP of 39.27\%, 10.73\%, 5.74\% and 1.18\%  for projects ZXing, SWT,AspecJ and Eclipse respectively.
 
@@
 The encoding of the GRU hidden layers is pass to fit a logistic regression to predict the possibility of each components to be defected.
-\todo{draw the graph to show the deep structure}
+Figure \ref{dnn} illustrates the structure described above.
+
+\begin{figure}
+	\includegraphics[scale=0.35]{deep_structure.png}
+	\caption{Deep GRU network structure}
+	\label{dnn}
+\end{figure}
 
@@
 Large change (ex: doubling the embedding size) would result in huge memory requirement and failed in runtime.
-\todo {report performance }
+Our DRNN model achieve a MRR of 34.16\%, 67.92\%, 44.10\% and 11.81\%, and a MAP of 30.83\%, 51.13\%, 21.39\% and 6.53\%  for projects ZXing, SWT,AspecJ and Eclipse respectively.
 
@@
 Because if a developer knows a component very well, he should also has knowledge to the new added file to that component.
-After the truncation, there are\todo{add number} , , , , components in ZXing , SWT, Eclipse and AspectJ respectively. 
+After the truncation, there are 11, 15, 555 and 534 components in ZXing , SWT, Eclipse and AspectJ respectively. 
 We removed one bug from the SWT project since the defected file has no component level, it locates in the top most directory. 
@@
 For the project AspectJ and Eclipse, given the large  number of components, we report the top-10 bug hit rate.
+
 As shown in Table \ref{performance_top_k}, All models acheive 100\%  bug hit for the project ZXing, DRNN achieves the best result in all other three projects.
@@
 As shown in Table \ref{performance_MRR}, VSM achieves the best MRR of 43.12\% for ZXing, but DRNN achieves the best MRR in all other three projects which are 67.92\%, 44.10\% and 11.81\% for SWT, AspectJ and Eclipse respectively.
-DRNN achieve 163.82\% more bugs hit on average than VSM.
+DRNN achieves 207.72\% higher MRR on average than VSM.
 
@@
  			\hline\hline
- 			ZXing& 43.12\%&34.16\% &52.62\% \\
+ 			ZXing& 43.12\%&34.16\% &\textbf{52.62\%} \\
 
- 			SWT & 19.45\% & 67.92\% & 58.63\% \\
+ 			SWT & 19.45\% & \textbf{67.92\%} & 58.63\% \\
 
- 			AspecJ &14.40\%  & 44.10 \% & 46.22\%\\
+ 			AspecJ &14.40\%  & 44.10 \% & \textbf{46.22}\%\\
 
- 			Eclipse &2.38\% & 11.81\%& 4.12\% \\
+ 			Eclipse &2.38\% & \textbf{11.81\%}& 4.12\% \\
 
@@
  \end{table}
+
+When comparing by MAP, same situation is observed. 
+VSM achieves better MAP in ZXing project which is 39.27\%, but DRNN achieves better result in all other three projects which are 51.13\%, 21.39\% and 6.53\% for SWT, AspecJ and Eclipse respectively. 
+DRNN achieves 320.27\% higher MAP than VSM on average.
 
@@
  			\hline\hline
- 			ZXing& 39.27\%&30.83\% &51.77\%\\
+ 			ZXing& 39.27\%&30.83\% &\textbf{51.77\%}\\
 
- 			SWT & 10.73\%  & 51.13\%  & 39.71\% \\
+ 			SWT & 10.73\%  & \textbf{51.13\%}  & 39.71\% \\
 
- 			AspecJ &5.74\% & 21.39\% & 15.69\%\\
+ 			AspecJ &5.74\% & \textbf{21.39\%} & 15.69\%\\
 
- 			Eclipse &1.18\% & 6.53\%& 1.97\% \\
+ 			Eclipse &1.18\% & \textbf{6.53\%}& 1.97\% \\
 
@@
 \subsection{Is RNN Better Than IR Methods in Mining Bug Report ?}
+Based on the fact that DRNN achieves better result in top-k bug hit, MRR and MAP in all three larger projects, it is reasonable to believe that DRNN is more suitable for learning from bug reports.
+Even for the smaller project ZXing, DRNN also achieves good result.
+Considering that we did not perform hyper-parameters tuning, DRNN has the potential to achieve even better result if we did that. 
+However, since DNN is a black box method, we don't know why it can achieve such a good result and to theoretically validate our assumptions, we can only do the judgment based on their performance. 
+Future work can be done to understand how DRNN combines syntactic and semantic information from bug reports to give the predictions.
 
 %\subsection{Is Ensembling Really Improve Performance}
+
+\section{Threat To Validity}
+We have showed some bug reports to illustrate how it is different from natural text.
+Bug reports contains natural text, code segment, error trace log which make it more difficult to learn than natural text or pure source code files which has a unique grammar.
+Based on this we confirm by comparing their performance on predicting defected components that DRNN are more appropriate to used for data mining bug reports.
+But bug reports in the industry could be very different from that in open source projects. 
+They can be more formalized and contains more important terms for IR methods to use. 
+We still need to perform similar experiment on bug reports from the industry to fully verify the conclusion. 
+However, we believe that natural text, code segments and error trace log are the three elements in bug reports even in the industry.
+
+DRNN is a black box method. 
+We don't truly understand why it can achieve such a good performance, how it combines semantic and syntactic information from bug reports to give out the predictions.
+The conclusion is only based on empirical observation on their performance and has no theoretical prove.
+Understanding the symbolic representation of DNN's mechanism is still an open question not only in software engineering community but in all fields that DNN dominants.
+
+\section{Conclusion}

### 2018-04-11 language_modeling/ptb_word_lm.py

@@ -52,7 +52,7 @@ $ tar xvf simple-examples.tgz
 
 To run:
 
-$ python ptb_word_lm.py --data_path=simple-examples/data/ --num_gpus=0 --save_path=/home/zhuyuecai/workspace/AITour/language_modeling/model_word_lstm/ --model=large
+$ python ptb_word_lm.py --data_path=simple-examples/data/ --num_gpus=0 --save_path=/home/zhuyuecai/workspace/AITour/language_modeling/model_char_elman/ --model=large --rnn_mode=ELMAN
 
 """
 from __future__ import absolute_import
@@ -93,7 +93,7 @@ FLAGS = flags.FLAGS
 BASIC = "basic"
 CUDNN = "cudnn"
 BLOCK = "block"
-
+ELMAN = "elman"
 
 def data_type():
   return tf.float16 if FLAGS.use_fp16 else tf.float32
@@ -372,7 +372,7 @@ class LargeConfig(object):
   lr_decay = 1 / 1.15
   batch_size = 80
   vocab_size = 10000
-  rnn_mode = BLOCK
+  rnn_mode = ELMAN
 
 
 class TestConfig(object):
@@ -389,7 +389,7 @@ class TestConfig(object):
   lr_decay = 0.5
   batch_size = 20
   vocab_size = 10000
-  rnn_mode = BASIC
+  rnn_mode = ELMAN
 
 
 def run_epoch(session, model, eval_op=None, verbose=False):
@@ -536,18 +536,16 @@ def main(_):
         sv.saver.save(session, FLAGS.save_path, global_step=sv.global_step)
   with open("./output.log",'w') as f:
       f.write("train perplexity:\n")
-      f.write(per_list)
       for item in per_list:
         f.write("%s," % item)
-      f.write("/n")
+      f.write("\n")
       f.write("="*12)
       f.write("validation perplexity:\n")
       for item in val_list:
         f.write("%s," % item)
-      f.write("/n")
+      f.write("\n")
       f.write("="*12)
       f.write("test perplexity:\n")
-      f.write(test_list)
       for item in test_list:
         f.write("%s," % item)
 

### 2018-04-14 defectLocalization/paper/paper_body.tex
add text

@@
 Analyzing the code base dramatically increase the learning time of this kind of algorithm in large projects.
-Moreover, the fast evolution of source code further penalizes this approach that the predictive model has to be updated frequently.   
+%Moreover, the fast evolution of source code further penalizes this approach that the predictive model has to be updated frequently.   
 In this paper, we explore the possibility to predict defected components solely based on information learned from bug reports.
@@
 Bug report is different from common text and source code in that it is generally composed by common text and source code segment or error trace message. 
-We believe that IR method and RNN can learn different information from bug reports and could complement each other.
+%We believe that IR method and RNN can learn different information from bug reports and could complement each other.
+In this work we want to find out whether deep Recurrent Neural Network can learn from bug report more efficiently than IR based method, namely the Vector Space Model. 
 Thus the ensemble of these two could offer better performance than using only one of them.
@@
 \begin{itemize}
-	\item an ensemble of naive tf-idf based VSM and Gated Recurrent Network to recommend high risk components solely based on bug reports.
-	\item By analyzing the performence of the naive tf-idf based VSM and Gated Recurrent Network on their own, and the ensemble of these two, we show that IR method and RNN can learn different information from bug reports and could complement each other to offer better performance in the ensemble method.
+	%\item an ensemble of naive tf-idf based VSM and Gated Recurrent Network to recommend high risk components solely based on bug reports.
+	\item an naive tf-idf based VSM method and a deep Gated Recurrent Unit Network to recommend high risk components solely based on bug reports.
+	%\item By analyzing the performence of the naive tf-idf based VSM and Gated Recurrent Network,  we show that IR method and RNN can learn different information from bug reports and could complement each other to offer better performance in the ensemble method.
+	\item By analyzing the performence of the naive tf-idf based VSM and Gated Recurrent Network,  we show that deep Recurrent Neural network achieves 163\% more bug hit by top-k recommendation, 2 times higher Mean Reciprocal Rank(MRR) and 3 times higher Mean Average Precision(MAP) and hence confirm the hypethesis that DRNN can learn better from bug reports.
 	\end{itemize}
+
+The paper is organized as the following:
 
@@
 
-In our DRNN implementation, the input layer pass the input vector to the embedding layer which generates the embedding of size $100$.
-The resulted embedding will then be passed to the stacked hidden GRU layers of size $10$.
+In our DRNN implementation, the input layer pass the input vector to the embedding layer which generates the :word embedding of size $100$.
+The resulted embedding will then be passed to the stacked hidden GRU layers of size $10$ with each GRU cell of size $100$.
 The encoding of the GRU hidden layers is pass to fit a logistic regression to predict the possibility of each components to be defected.
-Figure \ref{dnn} illustrates the structure described above.
+Figure \ref{dnn} illustrates the structure described above. All settings are selected by random withno specific reason.
 
@@
 
-\subsection{Ensemble of VSM and GRU}
-Ensemble method \cite{dietterich2000ensemble} is used to combine predictions from multiple different model to give out better performance than a single model.	
-\cite{lam2017bug} ,\cite{wang2014version} and \cite{jonsson2016automated} apply ensemble method to perform bug triage and achieve good performance. 
-Different schemes can be used in ensembling. 
-Stacked Generalization\cite{wolpert1992stacked} is theorectally the most effective one which adds one more classifier to take predictions from ensembled models as input and is trained to reduce prediction error.
-Jonsson \etal \cite{jonsson2016automated} ensembled TF-IDF with different ML algorithms with Stacked Generalization.
-However, as a preliminary research, we apply a simlper scheme 
-For a given component, we takes the minimum of the two risks given by the two aforemention models as the final risk.
-
-\begin{equation}
-risk(c) = min(risk_{VSM}(c) , risk_{DNN}(c) )
-\end{equation}
-
-\todo {report performace}
+%
+%\subsection{Ensemble of VSM and GRU}
+%Ensemble method \cite{dietterich2000ensemble} is used to combine predictions from multiple different model to give out better performance than a single model.	
+%\cite{lam2017bug} ,\cite{wang2014version} and \cite{jonsson2016automated} apply ensemble method to perform bug triage and achieve good performance. 
+%Different schemes can be used in ensembling. 
+%Stacked Generalization\cite{wolpert1992stacked} is theorectally the most effective one which adds one more classifier to take predictions from ensembled models as input and is trained to reduce prediction error.
+%Jonsson \etal \cite{jonsson2016automated} ensembled TF-IDF with different ML algorithms with Stacked Generalization.
+%However, as a preliminary research, we apply a simlper scheme 
+%For a given component, we takes the minimum of the two risks given by the two aforemention models as the final risk.
+%
+%\begin{equation}
+%risk(c) = min(risk_{VSM}(c) , risk_{DNN}(c) )
+%\end{equation}
+%
+%\todo {report performace}
 
@@
 Even for the smaller project ZXing, DRNN also achieves good result.
+One potential reason to explain why DRNN is not better than ZXIng is that, ZXing is a small project with only 20 bugs in total, and 16 bugs in the training set.
+The size of the training set is not enough for DRNN to learn a good model.
+Conversly, SWT, AspectJ and Eclipse has more bugs in the training data set which is sufficient for DRNN to learn a good model.
 Considering that we did not perform hyper-parameters tuning, DRNN has the potential to achieve even better result if we did that. 
@@
 
-\section{Threat To Validity}
+\section{Threat and Future Work}
 We have showed some bug reports to illustrate how it is different from natural text.
@@
 We don't truly understand why it can achieve such a good performance, how it combines semantic and syntactic information from bug reports to give out the predictions.
-The conclusion is only based on empirical observation on their performance and has no theoretical prove.
+The conclusion is only based on empirical observation on their performance and has no theoretical proof.
 Understanding the symbolic representation of DNN's mechanism is still an open question not only in software engineering community but in all fields that DNN dominants.   
+Moreover, since VSM performs better only for the project ZXing, finding the difference in bug reports between ZXing and the other three projects could help further understand how DRNN learns from bug reports.
+
+Training a Deep Neural Network is very time consuming especially when the training data set is large. 
+Future work on an online training algorithm for deep neural network would be very beneficial.
 

### 2018-04-14 defectLocalization/paper/paper_body.tex
draft paper

@@
 
- 		\begin{tabular}{c|l|l|l} %
- 			 \textbf{Projects} & \textbf{VSM} & \textbf{DRNN} & \textbf{Ensemble} \\
+ 		\begin{tabular}{c|l|l} %
+ 			 \textbf{Projects} & \textbf{VSM} & \textbf{DRNN}\\
  			\hline\hline
- 			ZXing(top-1)& 4(100\%)&4(100\%) &4(100\%) \\
+ 			ZXing(top-1)& 4(100\%)&4(100\%)  \\
 
- 			SWT(top-1) & 10(50\%) & \textbf{20(100\%)} &18(90\%)\\
+ 			SWT(top-1) & 10(50\%) & \textbf{20(100\%)} \\
 
- 			AspecJ(top-10) & 24(41.38\%)  & \textbf{46(79.31\%)} & 28(48.28)\%\\
+ 			AspecJ(top-10) & 24(41.38\%)  & \textbf{46(79.31\%)} \\
 
- 			Eclipse(top-10) &22(3.6\%) & \textbf{124(20.29\%)} & 26(4.26\%)\\
+ 			Eclipse(top-10) &22(3.6\%) & \textbf{124(20.29\%)} \\
 
@@
 
+%  \begin{table}[h]
+%  	\begin{center}
+%  		\caption{Top k bugs hit}
+%  		\label{performance_top_k}
+%  		
+%  		\begin{tabular}{c|l|l|l} %
+%  			\textbf{Projects} & \textbf{VSM} & \textbf{DRNN} & \textbf{Ensemble} \\
+%  			\hline\hline
+%  			ZXing(top-1)& 4(100\%)&4(100\%) &4(100\%) \\
+%  			
+%  			SWT(top-1) & 10(50\%) & \textbf{20(100\%)} &18(90\%)\\
+%  			
+%  			AspecJ(top-10) & 24(41.38\%)  & \textbf{46(79.31\%)} & 28(48.28)\%\\
+%  			
+%  			Eclipse(top-10) &22(3.6\%) & \textbf{124(20.29\%)} & 26(4.26\%)\\
+%  			
+%  		\end{tabular}
+%  	\end{center}
+%  \end{table}
+
 As shown in Table \ref{performance_MRR}, VSM achieves the best MRR of 43.12\% for ZXing, but DRNN achieves the best MRR in all other three projects which are 67.92\%, 44.10\% and 11.81\% for SWT, AspectJ and Eclipse respectively.
 DRNN achieves 207.72\% higher MRR on average than VSM.
+%
+% \begin{table}[h]
+% 	\begin{center}
+% 		\caption{Mean Reciprocal Rank(MRR)}
+% 		\label{performance_MRR}
+% 		
+% 		\begin{tabular}{c|l|l|l} %
+% 			\textbf{Projects} & \textbf{VSM} & \textbf{DRNN} & \textbf{Ensemble} \\
+% 			\hline\hline
+% 			ZXing& 43.12\%&34.16\% &\textbf{52.62\%} \\
+% 			
+% 			SWT & 19.45\% & \textbf{67.92\%} & 58.63\% \\
+% 			
+% 			AspecJ &14.40\%  & 44.10 \% & \textbf{46.22}\%\\
+% 			
+% 			Eclipse &2.38\% & \textbf{11.81\%}& 4.12\% \\
+% 			
+% 		\end{tabular}
+% 	\end{center}
+% \end{table}
 
@@
 
- 		\begin{tabular}{c|l|l|l} %
- 			\textbf{Projects} & \textbf{VSM} & \textbf{DRNN} & \textbf{Ensemble} \\
+ 		\begin{tabular}{c|l|l} %
+ 			\textbf{Projects} & \textbf{VSM} & \textbf{DRNN} \\
  			\hline\hline
- 			ZXing& 43.12\%&34.16\% &\textbf{52.62\%} \\
+ 			ZXing& 43.12\%&34.16\%  \\
 
- 			SWT & 19.45\% & \textbf{67.92\%} & 58.63\% \\
+ 			SWT & 19.45\% & \textbf{67.92\%}  \\
 
- 			AspecJ &14.40\%  & 44.10 \% & \textbf{46.22}\%\\
+ 			AspecJ &14.40\%  & 44.10 \% \\
 
- 			Eclipse &2.38\% & \textbf{11.81\%}& 4.12\% \\
+ 			Eclipse &2.38\% & \textbf{11.81\%} \\
 
@@
  \end{table}
-
 When comparing by MAP, same situation is observed. 
@@
 DRNN achieves 320.27\% higher MAP than VSM on average.
+
+% \begin{table}[h]
+% 	\begin{center}
+% 		\caption{Mean Average Precision(MAP)}
+% 		\label{performance_map}
+% 		
+% 		\begin{tabular}{c|l|l|l} %
+% 			\textbf{Projects} & \textbf{VSM} & \textbf{DRNN} & \textbf{Ensemble} \\
+% 			\hline\hline
+% 			ZXing& 39.27\%&30.83\% &\textbf{51.77\%}\\
+% 			
+% 			SWT & 10.73\%  & \textbf{51.13\%}  & 39.71\% \\
+% 			
+% 			AspecJ &5.74\% & \textbf{21.39\%} & 15.69\%\\
+% 			
+% 			Eclipse &1.18\% & \textbf{6.53\%}& 1.97\% \\
+% 			
+% 		\end{tabular}
+% 	\end{center}
+% \end{table}
 
@@
 
- 		\begin{tabular}{c|l|l|l} %
- 			\textbf{Projects} & \textbf{VSM} & \textbf{DRNN} & \textbf{Ensemble} \\
+		\begin{tabular}{c|l|l} %
+			\textbf{Projects} & \textbf{VSM} & \textbf{DRNN}  \\
 			\hline\hline
- 			ZXing& 39.27\%&30.83\% &\textbf{51.77\%}\\
+			ZXing& 39.27\%&30.83\% \\
 
- 			SWT & 10.73\%  & \textbf{51.13\%}  & 39.71\% \\
+			SWT & 10.73\%  & \textbf{51.13\%}   \\
 
- 			AspecJ &5.74\% & \textbf{21.39\%} & 15.69\%\\
+			AspecJ &5.74\% & \textbf{21.39\%}\\
 
- 			Eclipse &1.18\% & \textbf{6.53\%}& 1.97\% \\
+			Eclipse &1.18\% & \textbf{6.53\%} \\
 
@@
 \section{Conclusion}
+
+Precise bug localization could help improve the correctness of developer assignment in issue triage.
+Previous work focus on combining source code information, versioning history and other complementary information with bug reports to improve the performance of risky file prediction.
+However, in companies with high code security policy, these information may not be available to bugs triage.
+In this work we perform bug localization by only learning from  bug reports and achieve acceptable performance. 
+Moreover, previous work applies IR based method to learn from bug reports. 
+Given the difference between bug reports and natrual text that bug report occationaly contains code segments, error trace log, 
+we believe deep recurrent neural network may be more capable in learning from bug reports.
+This is confirmed by the experiment comparing the performance of deep recurrent neural network and the TF-IDF with VSM on learning bug reports from four open source projects,
+ZXing, SWT, AspectJ and Eclipse. 
+Deep Recurrent Neural Network achieves on average 163\% more top-k bug hit, 207.72\% higher MRR and 320.27\% higer MAP than the VSM model.

### 2018-05-01 language_modeling/paper/document.tex
add paper

\documentclass[]{article}
\usepackage{authblk}
\usepackage{caption}
\usepackage{microtype}
%\usepackage{amsthm}
\usepackage{graphicx}
\graphicspath{{figures/}}
\DeclareGraphicsExtensions{.pdf,.jpeg,.png}
%\usepackage{dsfont}
%\usepackage{amsmath}
%\usepackage{fancyvrb}
%\usepackage{color}
%\usepackage{algorithmic}
%\usepackage{array}
%\usepackage{mdwmath}
%\usepackage{mdwtab}
%\usepackage{eqparbox}
%\usepackage{fixltx2e}
%\usepackage{stfloats}
%\usepackage{float}
%\restylefloat{table}
%\restylefloat{graphicx}
\usepackage{url}
\usepackage{listings}
\usepackage{comment}

%opening
\title{}
\author{Yue Cai Zhu	}
%\authornote{Dr.~Trovato insisted his name be first.}
%\orcid{1234-5678-9012}
\affil{McGill University}
\affil {yue.c.zhu@mail.mcgill.ca}

\renewcommand\Affilfont{\itshape\small}

\begin{document}

\maketitle

\begin{abstract}

\end{abstract}

\section{Introduction}
Statistical Language Model(SLM) is a conditional probability distribution  of a sequence of linguistic  entities including words, phrases, characters.
It is widerly used to improve the performance of various natural language applications, such as speech recognition, text mining, spelling correction or recommendation and machine translation. 
The method to obtain a Statistical Language Model are well explored in the past 40 years\cite{rosenfeld1996maximum}\cite{breiman1984classification}\cite{jelinek1992basic}\cite{jelinek1992basic}.
Recently Mikolov et al. applied Recurrent Neural Network(RNN) in SLM and reported good performance\cite{mikolov2010recurrent}.
The model they applied is called the Elman network which is a simple kind of RNN and they believe that the ability of RNN to store past context is the key to its good performance.
However, the gradient vanishing problem\cite{hochreiter1998vanishing} in the training or the Elman network could potentially degrade its performance.  
The solution to this problem is a new type of RNN which is call Long Short Term Memory(LSTM)\cite{hochreiter1997long} and its variant Gated Recurrent Unit(GRU)\cite{cho2014properties}.
In this work, we are interested to see whether LSTM and GRU could outperform the Elman network in charactor level SLM, namely, is the gradient vanish problem is critical to charator level SLM.

Moreover, previous work focus on word level SLM and not much progress has been made for charactor level SLM. 
It is well believed that charactor level SLM requires less train data than word level SLM but to the best of our knowledge no formal experiment to support this argument.
Therefore, we are also interested to varify this argument.

The contributions of this paper is listed below:
\begin{itemize}
	\item Compare the performance of LSTM and GRU to the Elman net and verify that the gradient vanishing problem is not critical in charactor level SLM. Moreover, because charator level SLM only need short term history, the Elman network is actually more suitable to charactor level SLM.
	\item Veriy that charactor level SLM requires less training data than word level SLM 
\end{itemize}

The organization of the paper is as the following: section 1 briefly introduce the motivation of this work; 
section 2 introduce the background of SLM and charactor level SLM and propsed the two research questions of this paper; 
section 3 introduce the detail of the three types of Recurrent Neural Network used in the experients which is the Elman network, LSTM and GRU;
section 4 describe the experiment design, the pen-tree bank data set used in the experiemnts and the perplexity that used to evaluate the performance of the resulted SLMs.
section 5 report the experiemtn result and answer the proposed research questions.
section 6 summarizes this work.

\section{Background}

\subsection{Statistical Language Modeling}
In Natrual Language Processing(NLP), Statistical Language Model(SLM) is a probability distribution  of all possible sequence of linguistic  entities including words, phrases, characters\cite{rosenfeld2000two}. 
In Practice, a traditional task in SLM is to model the probability that a given linguistic  entity appears next after a given sequence of linguistic  entities. 
This could be defined as the conditional probability distribution $P(e_i| e_1,e_2,...,e_{i-1})$ of the next linguistic entities $e_i$ given a sequence of prior entities $(e_1,e_2,...,e_{i-1})$. 
%For example, given the sequence of words: "I love", an SLM may give out the possiblity of 70\% for the next word to be "you" and 5\% for the word "toilet".

Statistical Lanuguage Model is generally used to improve the performance of speech recognition, text mining, spelling correction or recommendation and machine translation. 
For example, in automatic speech recognition, given an acoustic signal, the goal is to find the sentence that is most likely to have been spoken. 
In this process, SLM serves as a prior distribution in the classifier.
Figure \ref{speech_recognition} illustrates how SLM is applied in speech recognition.

\begin{figure}
	\includegraphics[scale=0.5]{speech.jpg}
	\caption{Speech recognition\cite{daniela2013speech}}
	\label{speech_recognition}
\end{figure}

\subsection{Charactor Level Language Modeling }
By Charactor level language model, we obtain the conditional probability distribution $P(c_i|c_1,c_2,...,c_{i-1})$ where $c_i$ is the charactor locates in the ith position of a charactor sequence. 
It captures the instrinsic rules of constructing a valid word by charactors.
Charactor level language model can be used together with word level language model to better handle poems and songs, it can also be used in spelling correction or recommendation.
It is believed that charactor level language model require less training data than word level model because the small vocabulary size.
However, this has not been formally verified.
Most of the previous work focus on word level modeling or phrase level.
Because they can make use the semantic information learned from documents to give out predictions which make sense to human. 
Not much work for charactor level language modeling except for some charactor based languages such as Chinese and Korean.

\subsection{Research Questions}
In this work, we are trying to answer the following two research questions.

\textbf{RQ1: Is Charactor Level Language Model Requires Less Training Data Than Word level?} 
One critical requriement of word level language modeling is the need of enormous amount of documents to train a good model to learned the syntactic rule of a particular language and the semantic information from a given document.
Moreover, some rarely used words would be ignored by the model because its small frequency in the documents.
We can only include more documents with the hope that the rarely used words could get enough frequency count to be captured.
In contrast, charactor level language model just need to learn the instrinsic rules of constructing a valid words, given the small size of the set of available charactors in a language, it should require much less documents to train a good model. 
But is this argument really true?
We can only verify this by experiments.

\textbf{RQ2: Which Recurrent Network Is Better for Charactor Level Language Modeling?} 
Recurrent neural network is good in handling sequential data. 
Sentence and word are one type of sequential data. 
As shown by Mikolov et al.\cite{mikolov2010recurrent}, the Elman network could achieve exellent performance in language modeling.
But due to the gradient vanishing problem in training\cite{hochreiter1998vanishing}, the Elman network is less capable to remember long term history than Long Short Term Memory and Gated Recurrent Unit.
From the proposed argument in RQ1, charactor level language only need to learn the intrinsic rule of constructing words.
Is long term memory important for learning this intrinsic rule? 
Namely which Recurrent Network Is Better for Charactor Level Language Modeling?

\section{Methodology}
For the experiments, we implement the following three types of recurrent neural network: the Elman network, long short term memory and gated recurrent unit.

\subsection{The Elman Network}
The Elman network is one of the simplest recurrent neural network\cite{elman1990finding}. 
Its structure is shown in figure \ref{elman}.
\begin{figure}
	\includegraphics[scale=0.8]{elman.png}
	\caption{The Elman Network\cite{mikolov2010recurrent}}
	\label{elman}
\end{figure}

By adding the hidden context layer, the elman network is capable to take previous input together with the current input to give out prediction. 
Given the input embedding $w(t)$ at time $t$ of size $V$, the output layer concatenates the previous output of hidden context layer $s(t-1)$ of size $H$ as equation 1 to generate the output vector $x(t)$  of size $V+H$.
\begin{equation}
	x(t) = w(t)||s(t-1)
\end{equation}

where $||$ is the operation of concatenation. 
Then the output of the hidden context layer is updated by:
\begin{equation}
	s(t) = f(x(t)  \cdot u)
\end{equation}

where u is the weight for the hidden context layer and has size of $(V+H) \times H$ and $f()$ is the sigmoid function.
And $s(t)$ is also called the encoding of the recurrent network at time $t$ which will be passed to the output layer to generate the output $y(t)$:

\begin{equation}
	y(t) = g(s(t) \cdot v)
\end{equation}

where $v$ is the weight matrix for the output layer and has size of $H \times K$ given $K$ to be the size of $y(t)$. 
And $g()$ is the softmax activation function.
Notice that bias could be added to the updating of $s(t)$ and $y(t)$ in practice for more freedom in performance tuning.

The Elman network is capable to remember input history. 
However, due the the gradien vanishing/exploding problem, the impact of past history could eventually has no effect or takes major effect\cite{hochreiter1998vanishing}.
In order to solve this problem, another type of recurrent neural network which named long short term memory is proposed\cite{hochreiter1997long}.

\subsection{LSTM}
Long short term memory adds the input gate $i_t$, forget gate $f_t$ and output gate $o_t$ to control the remaining of backpropagated error which continuously feeds error back to each of the three gates until they learn to cut off the value. 
Thus, regular backpropagation is effective at training an LSTM unit to remember values for long durations.
Its structure is shown in figure \ref{lstm}.

\begin{figure}
	\includegraphics[scale=0.65]{lstm.png}
	\caption{Long Short Term Memory\cite{hochreiter1997long}}
	\label{lstm}
\end{figure}
Given the input vector $x_t$ at time $t$, the output gate $f_t$ is updated as:
\begin{equation}
	f_t = \sigma_g(W_fx_t + U_fh_{t-1} + b_f)
\end{equation}

The input gate $i_t$ is updated as:
\begin{equation}
	i_t = \sigma_g(W_ix_t + U_ih_{t-1} + b_i)
\end{equation}

And the output gate $o_t$:
\begin{equation}
o_t = \sigma_g(W_ox_t + U_oh_{t-1} + b_o)
\end{equation}

then the context layer $c_t$ is updated as:

\begin{equation}
c_t = f_t \circ c_{t-1} +i_t \circ \sigma_c(W_cx_t + U_ch_{t-1} + b_c)
\end{equation}

after the hidden context layer is updated, the output of the network is obtained by:
\begin{equation}
	h_t = o_t \circ \sigma_h(c_t)
\end{equation}

where $W$ , $U$ are the weight matrix for the corresponding gate,  $\circ$ is the point wise product operation and $\sigma$ is the sigmoid function .

\subsection{Gated Recurrent Unit}

GRU is proposed to solve the gradient vanishing problem in training a (RNN)\cite{chung2014empirical}.
It acheive the same performance as Long Short Term Memory but with less computations.
Its stucture is show in figure \ref{gru}. $h$ is the current state and $\hat{h}$ is context state which could memorize the impact of the input history. 
The reset gate $r$ controls whether the state from the current input should be memorized in $\hat{h}$.
The update gate $z$ controls whether the memory from $\hat{h}$ should considered when updating $h$ to give out prediction.  
\begin{figure}
	\includegraphics[scale=0.8]{gru.png}
	\caption{Gated Recurrent Unit\cite{chung2014empirical}}
	\label{gru}
\end{figure}

Given the input vector $x_t$ at step t, each gates and states are calcuated recursively as:
\begin{equation}
z_t = \sigma_g(W_zx_t+U_{z}h_{t-1}+b_z)
\end{equation}	
\begin{equation}
r_t =  \sigma_g(W_rx_t+U_{r}h_{t-1}+b_r)
\end{equation}	
\begin{equation}
h_t=(1-z_t) \circ h_{t-1} + z_t \circ \sigma_h(W_hx_t+U_{h}(r_t \circ h_{t-1})+b_h)
\end{equation}
Where $o$ is point-wise multiplication, $W$ and $U$ is the weight matrices for the corresponding component, $b$ is the bias vector.
$\sigma_g$ is the sigmoid activation function which has the form:
\begin{equation}
\sigma_g(x) = \frac{1}{1+e^{-1}}
\end{equation}
and $\sigma_h$ is the hyperbolic tangent activation function with the form:
\begin{equation}
\sigma_h(x)=\frac{e^x - e^{-x}}{e^x + e^{-x}}	
\end{equation}

\section{Experiment Design and Evaluation}

\subsection{Data and Settings}
We use the Penn TreeBank data set in our experiment. 
The Penn TreeBank data set is commonly used to evaluate statistical language models.
It is generated from 2,499 Wall Stree stories which have in total $1,000,000$ words and a vocabulary of size $10,000$.
There are $49199$ sentences in the data set and they are separed to three data set, the training, validating and testing data set.
The training data set has $42068$ sentences with $887521$ words.
The validating set has $3370$ sentences with $70390$ words. 
And the testing set has $3761$ sentences with $78669$ words.

All neural network are train with the same settings with the same structure which consists of two hidden states of size $1500$.
They are trained in 10 epochs with batch size of 80. 
The initial learning rate is 1 and decays after 3 epochs by rate of 0.870.
For regularizing, the drop out keep probability is 0.35.

\subsection{Perplexity}
The performance of the three neural network is evaluated by the metric perplexity. 
Perplexity is used to evaluate how complex a language model is. 
Given a unseen sentence $w_1w_2w_3...w_n$, the perplexity of a language model $P(w_1w_2w_3...w_n)$ is defined as:
\begin{equation}
	P(w_1w_2w_3...w_n)^{\frac{1}{n}} = (\prod_{i=1}^{n}P(w_i|w_1w_2...w_{i-1}) )^{\frac{1}{n} }
\end{equation}

The languange model with the lower perplexity is better.

\subsection{Experiments}
To anwer RQ1, we train a word level language model with LSTM on the full training set, then a charator level language model. 
After that, we reduce the training set by half and repeat the same process with the same validation and testing data set. 
By comparing the perplexity calculated from the testing data set, we found that charator level language model retain the same level of perplexity with half of the training set.
But the word level language model recieve a higher perplexity with half of the training data set.

For RQ2, we train the Elman network, LSTM and the GRU with the same data set and compare the resulted perplexity.
We found that the Elman network recieves the lowest perplexity, and LSTM recieves the same level of perplexity as that of GRU.

\section{Result and Discussion}

\subsection{RQ1: Is Charactor Level Language Model Requires Less Training Data?}

\subsection{RQ2: Which Recurrent Network Is Better for Charactor Level Language Modeling?}

\section{Conclusion}

\bibliographystyle{acm}
\bibliography{bibliography}
\end{document}
